ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-28 pyked.tex
minor wording fix

The \ck{} file used in this example can be found in the \pybox{tests} directory of the \pk{}
repository\footnote{\url{https://github.com/pr-omethe-us/PyKED/blob/master/pyked/tests/testfile_st_p5.yaml}}.
The data in this file comes from Stranic et al.~\autocite{Stranic:2012}, describing
shock-tube ignition delays for \textit{tert}-butanol. We have omitted the file
meta information below for space; the format is largely similar to the example in Section~\ref{sec:rcm-modeling}.
%
In this \ck{} file, multiple data points are specified with some common
conditions, including a common mixture composition and common definition of
ignition delay. Therefore, a \yabox{common-properties} section is specified.
%
\begin{yamlbox}
common-properties:
  composition: &comp
    - species-name: t-butanol
      InChI: 1S/C4H10O/c1-4(2,3)5/h5H,1-3H3
      mole-fraction: 0.003333333
    - species-name: O2
      InChI:  1S/O2/c1-2
      mole-fraction: 0.04
    - species-name: Ar
      InChI:  1S/Ar
      mole-fraction: 0.956666667
  ignition-type:  &ign
    target: OH* concentration
    type: 1/2 max
\end{yamlbox}
%
This block utilizes the ability of YAML files to define an anchor using the
\yabox{&} symbol and refer to that section later using the \yabox{*} symbol, as
can be seen in the definition of the \yabox{datapoints} section:
%
\begin{yamlbox}
datapoints:
  - temperature: 1459 kelvin
    ignition-delay: 347 us
    pressure: 1.60 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1389 kelvin
    ignition-delay: 756 us
    pressure: 1.67 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1497 kelvin
    ignition-delay: 212 us
    pressure: 1.55 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1562 kelvin
    ignition-delay: 105 us
    pressure: 1.50 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
\end{yamlbox}

>>>>

The \ck{} file used in this example can be found in the \pybox{tests} directory of the \pk{}
repository\footnote{\url{https://github.com/pr-omethe-us/PyKED/blob/master/pyked/tests/testfile_st_p5.yaml}}.
The data in this file comes from Stranic et al.~\autocite{Stranic:2012}, describing
shock-tube ignition delays for \textit{tert}-butanol. We have omitted the file
meta information below for space; the format is largely similar to the example in Section~\ref{sec:rcm-modeling}.
%
In this \ck{} file, multiple data points are specified with some common
conditions, including a common mixture composition and common definition of
ignition delay. Therefore, a \yabox{common-properties} section is specified.
%
\begin{yamlbox}
common-properties:
  composition: &comp
    - species-name: t-butanol
      InChI: 1S/C4H10O/c1-4(2,3)5/h5H,1-3H3
      mole-fraction: 0.003333333
    - species-name: O2
      InChI:  1S/O2/c1-2
      mole-fraction: 0.04
    - species-name: Ar
      InChI:  1S/Ar
      mole-fraction: 0.956666667
  ignition-type:  &ign
    target: OH* concentration
    type: 1/2 max
\end{yamlbox}
%
This block uses the ability of YAML files to define an anchor with the
\yabox{&} symbol and refer to that section later with the \yabox{*} symbol, as
can be seen in the definition of the \yabox{datapoints} section:
%
\begin{yamlbox}
datapoints:
  - temperature: 1459 kelvin
    ignition-delay: 347 us
    pressure: 1.60 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1389 kelvin
    ignition-delay: 756 us
    pressure: 1.67 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1497 kelvin
    ignition-delay: 212 us
    pressure: 1.55 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1562 kelvin
    ignition-delay: 105 us
    pressure: 1.50 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
\end{yamlbox}
